Best practices for forecasting changes in biodiversity: an example using breeding birds

### 2017-08-23 manuscript/draft.Rmd
??
intro edit
We aren't accounting for uncertainty in model choice and eval

Previous efforts to predict future patterns of species richness, and diversity
more generally, have focused primarily on building species distributions models
[SDMs; @thomas2004; @thuiller2011; @urban2015]. In general, these models
describe individual species' occurrence patterns as functions of the
environment. Predictions about where each species will occur in the future are
made by using forecasts of future environmental conditions to generate
predictions from these models. These species-level predictions are then combined
("stacked") to generate forecasts for species richness [e.g. @calabrese2014].
Alternatively, models that directly relate spatial patterns of species richness
to environment conditions have been developed and generally perform equivalently
to stacked SDMs [@algar2009; @distler2015]. This approach is sometimes referred
to as "macroecological" modeling, because it models the larger-scale pattern
(richness) directly [@distler2015]. [SDMs; @thomas2004; @thuiller2011;
@urban2015]. In general, these models describe individual species' occurrence
patterns as functions of the environment. Given forecasts for environmental
conditions, these models can predict where each species will occur in the
future. These species-level predictions are then combined ("stacked") to
generate forecasts for species richness [e.g. @calabrese2014]. Alternatively,
models that directly relate spatial patterns of species richness to environment
conditions have been developed and generally perform equivalently to stacked
SDMs [@algar2009; @distler2015]. This approach is sometimes referred to as
"macroecological" modeling, because it models the larger-scale pattern
(richness) directly [@distler2015].

Despite the emerging interest in forecasting species richness and other aspects
of biodiversity [@jetz2007; @thuiller2011], little is known about how
effectively we can anticipate these dynamics. This is due in part to the long
time scales over which many ecological forecasts are applied [and the resulting
difficulty in assessing whether the predicted changes occurred; @dietze2016].
What we do know comes from a small number of hindcasting studies, where models
are built using data on species occurrence and richness from the past and
evaluated on their ability to predict contemporary patterns [e.g., @algar2009;
@distler2015]. These studies are a valuable first step, but lack several
components that are important for developing forecasting models with high
predictive accuracy, and for understanding how well different methods can
predict the future. These "best practices" for effective forecasting and
evaluation (Box 1) broadly involve: 1) expanding the use of data to include
biological and environmental time-series [@tredennick2016]; 2) accounting for
uncertainty in observations, processes, model choice, and forecast evaluation
[@clark2001; @dietze2017]; and 3) conducting meaningful evaluations of the
forecasts by hindcasting, archiving short-term forecasts, and comparing
forecasts to baselines to determine whether the forecasts are more accurate than
assuming the system is basically static [@perretti2013].

>>>>

Previous efforts to predict future patterns of species richness, and diversity
more generally, have focused primarily on building species distributions models
[SDMs; @thomas2004; @thuiller2011; @urban2015]. In general, these models
describe individual species' occurrence patterns as functions of the
environment. Given forecasts for environmental conditions, these models can 
predict where each species will occur in the future. These species-level 
predictions are then combined ("stacked") to generate forecasts for species 
richness [e.g. @calabrese2014]. Alternatively, models that directly relate spatial 
patterns of species richness to environment conditions have been developed and 
generally perform equivalently to stacked SDMs [@algar2009; @distler2015]. 
This approach is sometimes referred to as "macroecological" modeling, because it 
models the larger-scale pattern (richness) directly [@distler2015].

Despite the emerging interest in forecasting species richness and other aspects
of biodiversity [@jetz2007; @thuiller2011], little is known about how
effectively we can anticipate these dynamics. This is due in part to the long
time scales over which many ecological forecasts are applied [and the resulting
difficulty in assessing whether the predicted changes occurred; @dietze2016].
What we do know comes from a small number of hindcasting studies, where models
are built using data on species occurrence and richness from the past and
evaluated on their ability to predict contemporary patterns [e.g., @algar2009;
@distler2015]. These studies are a valuable first step, but lack several
components that are important for developing forecasting models with high
predictive accuracy, and for understanding how well different methods can
predict the future. These "best practices" for effective forecasting and
evaluation (Box 1) broadly involve: 1) expanding the use of data to include
biological and environmental time-series [@tredennick2016]; 2) accounting for
uncertainty in observations and processes, [@harris2015; @yu2010]; and 3)
conducting meaningful evaluations of the forecasts by hindcasting, archiving
short-term forecasts, and comparing forecasts to baselines to determine whether
the forecasts are more accurate than assuming the system is basically static
[@perretti2013].
